Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2016-10-21 paper.tex
update

\title{A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition}

@@

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, and Semantic matchmaking is to discover interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is the another challenge with consideration in non-functional attributes, such as quality of service (QoS). Nowadays, many scholars have looked into optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that a comprehensive quality evaluation model is proposed to deal with finding optimised semantic web service composition solution. This paper develops a more applicable approach dealing with a comprehensive quality ---semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from the concept of functions to units and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual service and semi-automated web service composition are considered to be lower efficiency while automated web service composition is considered to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. Adding semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding one of the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts at the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. Howevever, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic matchmatching as optimised web service composition sollutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic matchmatching quality.

The overall goal of this paper is to develop an comprehensive evaluation model in  automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs(sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

\begin{enumerate}
 \item To address semantic matchmaking quality with considering different matching types associated with corresponding semantic similarity, which is demonstrated as a comprehensive quality --- a more general and applicable evaluation method utilising semantic information of service descriptions in this paper.

 \item To apply PSO for sorting an optimised service queue as a indirect representation of web service composition with consideration in optimising the comprehensive quality, this indirect representation is decoded using graph building algorithm to generate a service composite solution.

 \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. One part is that a given input or input set to get the desired output or output set, it typically refers to a statement in functional requirement ; another part specify the overall acceptable composite quality, which covers aspects in non-functionality. To accomplish the first half goal, two stages are involved in the investigation of this paper : services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given Task until the desired output found. It results in more than one solutions without considering optimisation; Service selection is to select web services to reach global best quality($T_{QoS}$). We are aiming to optimise a combined objective function involving both functional and non-functional concerns. Particularly in this paper, two challenges mentioned in Sect. \ref{introduction} are addressed in semantic web composite approach. First, the inputs of each service could be semantically matched by predecessor services in the composition. Second, optimisation in QoS would not be sufficient in many scenarios to make a good decision, if customers are looking for a trade off either in better service quality with counteroffer in QoS or better QoS with less strict functional matchmaking quality.

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service discovery process is to discovery the services an input-output concept matchmaking according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}. We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.

@@

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust and valid matches will be used to discover web service candidate for a service composition.

\subsection{Quality of Service and Composition Constructs}\label{web service selection}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements. This problem have been explored in optimising both single objective and multi-objectives in QoS. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as following:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: sequence and parallel are used in building the composite flow, which are described as follows:

@@

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements and negect non-functional requirements. This approach utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, which is expressed in ontologies, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting is introduced in a Ontology in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, where $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}. And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}. They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$, either 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection) associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system. for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable evaluation model in a full automated semantic web service composition.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. GP-based approach utilises tree representations, on which service as represented as terminal nodes, and composite constructs as the functional nodes. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is looked for using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition. However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model automated QoS-ware semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1:The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in terms of functional and non-functional requirement. The previous functional one is defined as $F(T_{Input}, T_{Output})$ , and the later nonfunctional one is the users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services and their relationship in semantic matchmaking to get prepared for designing service composition via building graphs. This step selects relevant web services related to services request. This leads to a shrunken service repository that is used by PSO-based algorithm. Step 3: a service composition graph is randomly built up with considering the QoS and matchmaking quality. This graph building is interleaved with semantic matchmaking for services. The output of one service and its associated input of another service is calculated in the matchmaking phase where semantic matchmaking quality are measured which will be explained in Subsection \ref{qualityModel}. Step 4,5: The optimisation of service composition solution is performed over the PSO in Section \ref{pso_algorithm}, which is used to find optimised particle locations mapped back to web service for service-graph building. This approach \cite{da2016particle} is an indirect representation of web service composition that constructing a graph-based composite service composition.
\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.

>>>>

\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}

@@

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. An optimisation problem is another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balancing between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimising composition solution. This paper develops a more applicable approach for comprehensive quality in semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value --- added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems - diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual service and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. Those semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts at the semantic level of web service composition. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match matching as web service composition solution. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and a few structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

\begin{enumerate}
 \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality integrated with QoS --- a more general and applicable evaluation model utilising semantic information of web services in this paper.

 \item To apply PSO for sorting out an optimised service queue as a indirect representation of web service composition with consideration in comprehensive quality, and this service queue is decoded using graph building algorithm to generate optimised comprehensive quality awareness   composite solution.

 \item To Compare the performance of comprehensive quality awareness service composition with the QoS-awareness utilising the benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is  a given task input or input set to get the desired Task output or output set, it typically refers to a statement of user's functional requirement; another nonfunctional part specifies the acceptable composite quality of service. To accomplish the composte goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$, and updated $T_{Input}$ with found services output, which is used to further discovery more related services until the desired $T_{Output}$ found. It normally results in more than one solutions. Service selection is to select one of those composite solution considering closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}
The semantic service matchmaking aims to discover appropriate services from service repository relevant to a customer's functional request defined by the Goal. A semantic web service is defined by $S(F(S_{Input}\in C_{1}, S_{Output}\in C_{2}), NF(S_{QoS}))$ with both Input and Output are linked to concept $C_{1}$ and $C_{2}$ in an ontology ($O$) respectively, satisfying $O=\{C, Tax\}$. The web service matching process is to pair the two services' output and input concepts according to the Taxonomy(Tax) within an ontology (O). To measure the quality of semantic matchmaking, different matching levels that are typically considered in the literature \cite{paolucci2002semantic}: We defined two web services associated with parameters in a particular domain: $S_{1}$ $(F(S_{Input}\in C_{1}, S_{Outputs}\in C_{2}), NF(S_{QoS}))$ and  $S2$ $(F(S_{Input}\in C_{3}, S_{Output}\in C_{4}), NF(S_{QoS}))$ and an Ontology($O$) with $C_{1},C_{2},C_{3}$, and $C_{4}$ defined in.

@@

Note that, to find relevant services to automatically form suitable and applicable service compositions for a given goal, we consider Exact, Plugin and Fail match types in our paper. Therefore, these three robust and valid matches will be used to discover web service candidates for a service composition.

\subsection{Quality of Service and Composition Constructs}\label{Quality of Service and Composition Constructs}
Currently, most of the optimisation problems \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} in web service composition are focusing on QoS optimisation, which covers aspects in non-functional requirements. This problem have been explored in both single objective and multi-objectives optimisation. Ideally, customers prefer lowest execution cost with highest response time and reliability. According to \cite{zeng2003quality}, four most often considered QoS parameters are as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for web services composition varies with respect to different constructs, which explains how services associated with each other \cite{zeng2003quality}. Here we consider two composite constructs: both sequence and parallel construts are used in building the composite flow, which are described as follows:

@@

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output concepts of web services to ensure a semantic matchmaking. Since semantic descriptions are introduced into web service, the semantic matchmaking is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}. In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, which utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}. And Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are also required to be pre-calculated in Formula \ref{equation2}. They chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined DL in the knowledge representation system. for example, both service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2 are needed. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable comprehensive quality model in a full automated semantic web service composition.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then the web services in this service queue are selected to build up a graph representation of web service composition. However, the composite solution does not distinguish different match types and the degree of matching, which could lead to the data returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the data requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and their similarity when evaluate an overall quality of composite service.

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO based approach, which is considered to be simple and efficient without penalising and repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is the users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that is used by PSO as a searching space. Step 3: a service composition graph is randomly built up interleaving with semantic matchmaking, where web services are discovered and connected with calculation of matchmaking quality, which will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web service is performed over the PSO in subSect. \ref{pso_algorithm}, which is used to find global best particle location mapped back to a service queue for a graph building. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking}
The semantic matchmaking is achieved by utilising semantic annotation with OWL and OWL-S. In this paper, we use MECE ontologies \cite{bleul2008self} XWL format, which could be considered to be an alternative form of ontology for services. In OWL, semantics specifies the both concepts and individuals in the forms of classes and instances but limited to taxonomies. The semantic concepts are expressed with the their statements and relationship in RDFs (such as subClassOf ), and the semantic individuals are related to the input and output parameters of web services. The MECE is an extensive annotation to WSDL files, which defines the each parameter of services associated with their semantic individuals. The overall matching making process is demonstrated in Figure \ref{matchmaking}.
